\documentclass[char]{Sel}
\begin{document}
\name{\cCarminis{}}
You're not a lich, but you're not human, either. You never seem to do things the right way around.

You remember little of your parents, besides that your father was a human man and your mother an elvish woman, bound by a love that defied social convention, not to mention genetics. They died in a tragic accident when you were still young, and so you grew up as an orphan, darting between earth and assorted demiplanes, hustling for shelter, scrounging for food in trash cans, just barely avoiding death by starvation or sickness or street violence.

Because of the odd mix of blood in your veins, you've always had an extraordinary knack for picking up magic, despite your lack of formal training. You've been able to make potions "that only vampires make," and perform rituals "that only work for trained witches," so on and so forth. You can pull off grand feats of magic even without many of the prerequisites, so perhaps it's no surprise that, when you picked up a few scraps of black magic, you found you could prepare an ordinary blue pen to be a phylactery and advance towards becoming a lich without actually committing any murders.

A few years back, your tinkering with dark magic oddly backfired-- you were attempting to turn a stone into a frog and ended up turning yourself into a toad instead. Fortunately, the mishap gave out a massive burst of magical energy that got another spellcaster's attention. Thus you met Tyran.

Tyran swooped in with countercharms-- that did involve a kissing you in toad form, for the record-- and saved you, and you’ve been half in love from that first meeting. Tyran is everything you're not-- worldly, eloquent, confident, focused. Yet you impressed Tyran in your own way. Apparently your sheer magical virtuosity is pretty damn captivating.

Tyran committed the murders required to become a lich as a vigilante, finding solid data to justify each death as helpful to the greater good. While you're still not thrilled about murders under any circumstance, those reasons are as airtight as you can imagine, so you've made your peace with Tyran's bloody history. You've also told Tyran about your aimless past and been answered with sympathy and a promise that you need never fear for your life again.

Tyran marveled at your progress with your phylactery, pleased that you too could become a lich, but then you had to face an unfortunate fact-- you are going to die off from old age before you finish your phylactery, unless you revert to the usual road and begin killing. You sensed that the only way you can achieve immortality without violence is to interact with as many liches as possible, soaking up their auras and observing their magic in the hopes that you can pick up their ways. You informed Tyran of your conundrum, and the two of you ultimately hatched a plot to provide you with said interaction.

This is how you've ended up posing as a lich, adapting a ghoul incantation into a spell that fools the typical lich detection charm, and entering the Society. So far, you've successfully met with Domin to do the initial paperwork, and you passed yourself off there well enough. Now you have to attend this convention and study a broad range liches, so you need to learn as much about their magic without exposing yourself as a human. If you successfully transform into a lich, you'll be glad to remain in the Society, because their dedication to relatively nonviolent lifestyles speaks to you. You firmly support the Society, but there's one aspect of the rules that worries you, though-- they explicitly protect members of the Society from harm, but not non-members. As a result, if you get discovered and kicked out before becoming a lich, it's open hunting season, and you can be rather easily killed and drained of your lifeforce.

Despite the risk, you are thankful to Tyran for supporting you in this plan, and you attempted to repay the favor with your resolution. You nominated Tyran for Senior member, and you fully intend to advocate for that resolution. You expect Domin, the Society’s Leader, will be a powerful ally in the cause-- Tyran suspects Domin has also submitted this promotion for consideration, and you really only put your resolution to be absolutely certain.

You trust Tyran implicitly-- after all, you're both taking a risk by smuggling you in tonight-- yet your relationship has become strained as the convention approaches. Recently, you've noticed an odd chill in your conversations, as if some new worry weighs on Tyran's mind. Have you given offense? You hope to be of assistance to Tyran if at all possible and atone for any mistake you may have made. Unfortunately, Tyran tends to be secretive, so you must drill through that cool demeanor and discover the true ailment before you devote your not insignificant magical skill to mending it . . .

\begin{itemz}[Notes]
  \item The resolution you submitted immediately pre-game was "Let Tyran become a Senior member."
      \item You have 18 units of power at the start of the game.
   \item Though you are not entirely human, your magical abilities match those of a human sorcerer. Follow the rules for a human sorcerer when performing magic.
   \item You own a booby-trapped fifty-dollar bill, a booby-trapped panpipe, the blue pen you have prepared to be your phylactery, an ordinary Pixel phone, and a peach.
    \end{itemz}
   
  
    
 \begin{itemz}[Goals]
\item Study magic and become a lich
\item Figure out why Tyran is upset and fix the issue
\item Promote Tyran to Senior member 
\item Offer your support to the Society's values
\end{itemz}

\end{document}
