\documentclass[char]{Sel}
\begin{document}
\name{\cDomin{}}

True name: Immundum (previously “Taeterri”)

You are known as Domin, creator and Leader of the Society of Ethical Liches. As a human you were an assassin, willing to kill anyone if sufficiently well-paid, and you used those murders to elevate yourself to immortality. You have since renounced your bloody ways, and now you take your position as a guiding light among liches seriously. You hope to spread the Society's values to more liches and build bridges among your kind, in addition to forming alliances with other species who have long spurned you.

Tyran is your most ardent supporter, and you return the warm feelings. Tyran made the transition from a fledgling human sorcerer to a lich as a vigilante, using magic to track down heinous human criminals and bring deadly justice to them. That sort of righteousness fits well with the Society's values, and so you gladly accepted Tyran into the fold. More recently, on the recommendation of gnomish friends you recruited Sollers, whose clever mind is a clear asset to the Society. You are thrilled with Sollers' latest invention, which seems to be a revolutionary breakthrough in phylactery research.

You enjoy your role as a leader of this fine organization. Indeed, you enjoy your whole existence as a lich, even the time you spend masquerading as a human. Yet there are certainly some dark moments. A few months back, you realized that your phylactery was becoming drained at an alarmingly fast rate, as if you were still a human. After running a battery of obscure tests with help from a specialist dwarf, you learned it had been cursed! You paid the price and transferred your power to a new phylactery, receiving a new true name, and now you are left sadly weak. You thought it would be at odds with the first rule of the Society to go on a killing spree to replenish your power, so you are anxious to find Members at this convention who will donate some energy to you. Hopefully, you might also find some answers about who cursed your phylactery, and why.

Furthermore, you strongly feel that the Society should vote at this convention to make the protection of phylacteries against corruption its research priority, to protect others from feeling the same dread you did. As a result, you decided to introduce this objective as a resolution. Additionally, you decided to recognize tonight's outstanding research breakthrough with a resolution recommending Sollers for a position as a Senior member. You have long held that Tyran deserves to become Senior member as well, but that will have to wait until a future century-- Sollers has objectively done more to advance the Society's values and is more deserving of a promotion, in your view. You will not back down in advocating for your two resolutions, but you hope to find some other favor you may pay Tyran.

You wish to reconnect with Tyran and all the other members of the Society, since you take your position as Leader and mentor seriously, and you will gladly try to address their concerns and help them out of any trouble they encounter. You especially want to learn more about Carminis, your new Junior member, and give a warm welcome to the ranks of the Society. You’ve only ever met to do the paperwork before, and Carminis struck you as both mysterious and somewhat troubled-- surely there is some help you can provide?

Most importantly of all, you wish to protect the integrity of the Society and enforce its rules. On the most basic level, you must run the voting procedure and make sure resolutions are chosen in a timely and orderly fashion. Furthermore, if any Society member has in any way participated in the recent rash of senseless murders, you must find them and hold them accountable. You also wish to stay in power as the Society's leader, but if necessity pushes you from your position you will settle for making sure that whoever takes your place is as committed to the Society's values as you.
\begin{itemz}[Notes]
  \item Your true name is Immundum. Previously, it was "Taeterri."
    \item Your phylactery currently has 2 units of power. Please fill in the card inside your phylactery's envelope with this information before game.
  \item The resolutions you submitted immediately pre-game were "Let Sollers become a Senior member" and "Let the Society dedicate its research efforts for the next century to protecting phylacteries from corruption."
  \item You own a booby-trapped black pen, a booby-trapped iPhone 7, a phylactery in the form of a baseball, a chocolate truffle, and a yellow apple.
    \end{itemz}
    

     \begin{itemz}[Goals]
     \item Run the Society's voting procedures
 \item Pass your two resolutions
 \item Replenish your phylactery's power
\item Punish any Society members involved in the recent killing spree
\item Support the Society's other members, especially Tyran
\item Keep your position as Leader
\end{itemz}

\end{document}
