\documentclass[char]{Sel}
\begin{document}
\name{\cKorv{}}
You are known as Korv, once an exceptionally well-respected lich, now a laughingstock of the magical community. You became a lich as a mercenary, slaughtering hundreds on the battlefield, but you grew bored of the violence. It was too simple, too routine. You enjoy complications.

So you joined the Society, less because you dislike gratuitous killing than because the challenge of living without magic and posing as a lowly human attracted you. You spent your life playing a variety of humble roles on Earth-- starving artist, backup dancer, factory worker, window cleaner-- while also returning to the Society every century with pomp and circumstance, as one of the group's Senior members. You found the ironies terribly entertaining.

Your love of entertainment caused you to fall for Lock, a new Junior member, at the last Society convention. Lock was nothing if not dramatic-- headstrong, domineering, flamboyant. At first, you were thrilled to hand your heart and true name over, but you soon realized your mistake. Lock never returned your feelings, instead exploiting your power and treating you as a lowly servant to be ground underfoot. Though your existence on Earth, acting as a personal assistant to the C.E.O. Lock plays, was tolerable, you were mocked throughout the whole magical community, an ancient Senior member utterly dominated by a young upstart. It was too bitter an irony for even you to stomach.

Your love soon turned to resentment, and so you contacted an elven sage whom you knew back in your human days for help. He told you that you could secretly break the bond through the power of hate. Thus, you dwelled on every slight and let every insult fester, until one day Lock had no more power over you. When Lock speaks your true name, you are no longer affected or compelled to obey.

You have hidden your newfound freedom and kept on obeying Lock's commands, all the while looking for revenge. You hope to destroy your so-called "beloved" as recompense for your years of shame, perhaps through learning Lock's true name or orchestrating a humiliating removal from the Society. Ideally, you'll even manage to kill Lock off. And you may find an ally in your long-time friend Tyran, though outright violence may cool that alliance. Tyran's always been puzzlingly peaceful for a lich, a real lover of nonviolence . . . It was that entertaining hypocrisy that drew you to Tyran in the first place.

Your elven friend has rescued you from hell, but at a price. He has long opposed the Society of Ethical Liches-- while he tolerates individual liches, any organization of your kind threatens him-- and so he bound you by magic to help him dismantle it. He tells you that you should exploit Sollers' machine, because it is profoundly flawed. If allowed to run with too little energy, it may backfire and wreak havoc on the Society. He also informs you that Specter wishes to become Leader and is less than completely committed to ethics, and that the Society, thus far tolerated by other magical species, would be extinguished if Specter were to become Leader. As you have no particular love for the Society, you will gladly pursue both these routes, aided by the fact that Lock is already discontent with Domin's inflexibility and looking for a new Leader. If you do not do serious damage to the Society tonight, the elf warns he will come calling and exact a different price-- another decade in servitude, this time in an elven court. It wouldn't be the end of your world, but you'd hate to suffer yet another indignity.

You've already inflicted your first blow of sorts. While you are required to follow the Society's rules and "fulfill your voting obligations," you spat in the face of the spirit of the rules with the resolution you submitted. You might see whether you can actually get it passed somehow-- it'd be a valuable way to prevent actual Society business from being done. And it'd be a funny motto, at any rate-- "Liches be crazy." Ha.

Accurate, too.

\begin{itemz}[Notes]
  \item Your true name is Vetustius.
      \item Your phylactery currently has 7 units of power. It would have more, but Lock has forced you to expend your power over the past century. Please fill in the card inside your phylactery's envelope with the power level before game.
  \item The resolution you submitted immediately pre-game was "Let the Society adopt an official motto: 'Liches be crazy.'"
  \item You own a booby-trapped playbill, a booby-trapped handbill, a tangerine, a bag of freeze-dried ice cream, and a phylactery in the form of a franc.
    \end{itemz}
    
  
  
 \begin{itemz}[Goals]
\item Make Sollers' precious machine backfire
\item Grind Lock underfoot for a change
\item Elevate Specter to the Leader's position
\end{itemz}


\end{document}
