\documentclass[char]{Sel}
\begin{document}
\name{\cLock{}}
You've adored secrets as long as you can remember, especially secrets that help you get things done. As a human, you enjoyed delving into abstruse dark magic, and you had even more fun as a bounty hunter, tracking down slippery targets and bringing them back, dead or alive. You preferred "dead." Those deaths piled up, eventually letting you become a lich.

As an immortal creature, you've wanted to uncover hidden truths not only on Earth but on the linked demiplanes as well, but you found yourself stonewalled by the sheer stigma liches face. The hatred got to you, especially since you yourself aren't fully comfortable with the murders you've committed-- many of your victims were louses through and through, but a few were decent, occasionally even innocent of all the charges made against them. As a result, you gladly curtailed your killing and joined the Society of Ethical Liches, and you now find it easier, though still not easy, to weave yourself into other magical communities and soak up their secrets. While it's slightly irritating not to be able to use magic freely on Earth, you've established yourself as a powerful C.E.O., and so you can sate your lust for off-limits information just by following the intrigue of human industry.

You happened on an unusual stroke of luck at your first convention, just a century back. A Senior member, Korv, was taken in by your obvious self-confidence and proceeded to fall head over heels in love. One moment you were just talking, and the next Korv’s true name-- Vetustius-- popped into your head, because a Soul Bond had just formed between the two of you! You've taken full advantage of the bond, turning Korv into your "personal assistant" in front of humans and simply your servant otherwise.

Honestly, you wonder if you've taken too much advantage. Korv turns melancholy at times, and then you feel something suspiciously like guilt. Given that you also miss the sheer thrill and simplicity of working alone, you've stopped telling Korv quite as much of your plans and have stopped being quite so dependent. Furthermore, you have decided to attempt an act of mercy and submit a resolution about a new research initiative-- studying how to dissolve Soul Bonds-- and you fully intend to advocate for its passage. However, you'd like to make sure you can keep Korv's goodwill even if you part ways. For that matter, you'd like to earn the goodwill of as many other Society members as possible, especially those ranked higher than you, because connections bring information and information brings you happiness.

In addition to general networking, you've got a few more specific goals in mind for the convention, because this group of liches brings many mysteries to solve. First off, you suspect the wild murderer everyone's talking about will be present here today-- anyone who thinks Society members could never lash out so violently is fooling themselves. If you figure out who the murderer is, you'd like to turn them in, but you'd also consider keeping quiet and blackmailing them, if that's clearly the more advantageous option for some reason. Additionally, you've heard rumors from contacts in the elven community that one of the members tonight is not in fact a lich-- you assume someone got their phylactery destroyed and failed to mention that to Domin. Again, you'd like to uncover the imposter and either expose them to the public or just press them for something else.

Then there's the secret every lich walks around with-- a true name. It's a risky business, but you'd like to learn as many true names as possible. You've already gotten hold of one name, "Taeterri," that, according to a dwarf connection of yours, belongs to a member of the Society. Alas, she wouldn't say whose name it was, and no amount of gold would tempt her.

You'd love to grab hold of some of the other magical items every lich walks around with as well. Magical items are rare and rather expensive, and liches always carry a creative assortment around to deter pickpockets. Those are interesting artifacts in their own right, of course, but the protection they afford could save your life when you investigate in shadier settings. Ideally, you'll walk away tonight with a wealth of booby-trapped items, and you'll spend the next century altering them so they no longer impact you. You've already invented a spell that you can use to temporarily shield yourself from particularly annoying magical effects. In this quest you might pay special attention to Specter, whom you're sure has a nasty side-- you wouldn't be surprised if Specter's items may play particularly malicious tricks.

Finally, if you can get a promotion tonight, you intend to take it. You strongly suspect Korv nominated you for Senior member-- true love and all that. Regardless, you can always leapfrog into the Leader's role in a vote, and Domin's idealism and endless faith in friendship grates enough on your nerves that you wouldn't feel bad about seizing the role. As Leader, you'd indulge your lust for secrets like never before, worming your way behind closed doors, and you might dabble in more theoretical knowledge by promoting magical research. You'd gladly discard Domin's approach to the role-- namely, attempting to please everyone and build bridges at any cost.

Now becoming Leader isn't likely, but if you get hold of true names just about anything is possible . . .

\begin{itemz}[Notes]
  \item Your true name is Astrorum.
      \item Your phylactery currently has 11 units of power. You've managed to keep it this high because you've had Korv do most of your spellcasting instead. Please fill in the card inside your phylactery's envelope with your power level before game.
  \item The resolution you submitted immediately pre-game was "Let the Society dedicate its research efforts for the next century to dissolving Soul Bonds."
  \item You own a booby-trapped kazoo, a booby-trapped silver coin, a phylactery in the form of a rag doll, some dates, and some graham crackers.
    \end{itemz}
    
  
    
 \begin{itemz}[Goals]
 \item Network and climb up the Society's hierarchy
\item Investigate the recent murders
\item Find the imposter
\item Collect true names
\item Collect magical items that you can use for protection
\item Get your resolution passed
\end{itemz}

\end{document}
