\documentclass[char]{Sel}
\begin{document}
\name{\cSollers{}}
You are Sollers, an inventor and Junior member of the Society of Ethical Liches. Even as a young human, you enjoyed puttering around with all sorts of magic, light and dark and everything in between. You also practiced medicine for several decades, following the often shockingly inaccurate customs of the time. You let blood and prescribed toxins as medicine, all while strongly suspecting that these practices, widely believed to save lives, were actually deadly. You didn't really consider yourself a murderer, and yet one day you transformed into a lich.

You kept right on practicing "medicine" and drawing on your deceased patients' lifeforces to fuel magical experiments, often working with the help of a colony of rogue gnomes, inventive creatures who recognized your genius and accepted you despite being a lich. Domin heard of your magical prowess through them, and suddenly you were invited to join the Society of Ethical Liches!

The code appeals to you, to the do-gooder in you that wanted to become a doctor in the first place. Domin promised you access to libraries and material and resources that could help compensate for the power you gave up by limiting your murders, and so you decided to give the Society a try. You've largely liked the experience, especially since the last convention voted to focus on charging phylacteries for the entirety of the last century, devoting a wealth of resources to this particular project. You thought this convention would be even more enjoyable, since you've used those resources to make a phylactery charging machine that runs on power sources besides lifeforces-- long considered an impossible feat. You planned to soak up your peers' praise and well-deserved recognition. Indeed, you fully intended to capitalize on your success and nominate yourself for Senior member, since a promotion will open even more doors through the magical world and further extend your research capabilities.

Then you had to face the fact that, even to a master practitioner like you, magic is complex and intractable and unfathomable.

You were performing a routine check on the machine just last night, testing the central potion, redoing your calculations, when you realized that the latest version of your machine involves a previously unknown element of randomness. It might charge phylacteries without drawing on any outside power source, but it might fail instead, providing no charge at all. You haven't called off the unveiling entirely though, because you found a way to reduce the chance of any such mishap-- you must simply reinforce the machine with as much outside power as you can. Fortunately, the setting of tonight's convention, Crescent Grove, is filled with deposits of pixie dust, which are power sources that you can attach to the machine. In the off-chance that someone dies tonight, you could also hook up their lifeforce. If you gather enough energy, you can rescue your machine and reclaim your grand moment, and the other liches, all ignoramuses compared to you, will never know the difference.

But forget them for a moment-- you yourself are upset by the uncertainty surrounding your machine, by the fact that you no longer understand exactly how your creation works. You should try and improve your understanding of magic as a whole in order to grasp its workings. In the short term, you should seize the opportunity to observe various styles of spellcasting at the convention-- watching other liches use magic is always enlightening. To perfect this machine in the long run, you've given up your old plans of becoming Senior member and instead submitted a resolution that will allow you to spend another century improving the machine. The extension will let you eliminate the randomness so it works reliably every time. You hope you can pass that resolution, though admitting that the machine doesn't already work exactly as intended will be a hit to your pride. In case it doesn't pass, though, you'd settle for another research objective studying liches or phylacteries, since the Society’s default objective-- helping still-human sorcerers become liches more efficiently-- doesn’t quite appeal to you. Sometimes you wish the Society focused even more on research, but perhaps you shouldn't complain. After all, few rarely have as many opportunities as you.

You've got one last goal for the night-- trivial by comparison, but entertaining nonetheless. Your friends among the gnome community whisper that the Society's newest addition, Carminis, is utterly devoted to Tyran. Some speculate that Carminis is Soul Bonded to Tyran, and you'd love to get proof of whether this is true or not. The gnomes have supported your experiments for so long, this little nugget of gossip would only begin to provide proper recompense . . .
\begin{itemz}[Notes]
  \item Your true name is Volantium.
      \item Your phylactery currently has 8 units of power. Please fill in the card inside your phylactery's envelope with this information.
  \item The resolution you submitted immediately pre-game was "Let the Society dedicate its research efforts for the next century to further improving Sollers' charging machine."
  \item You own a booby-trapped mechanical pencil, a booby-trapped nickel, a bottle of Sriracha hot sauce, a rice-crispy treat, and a phylactery in the form of a scrap of red silk.
    \end{itemz}


 \begin{itemz}[Goals]
 \item Study lich magic to better understand your machine
\item Supply your machine with extra power sources
\item Get an interesting research resolution-- preferably yours-- passed
\item Investigate Carminis' relationship to Tyran
\end{itemz}

\end{document}
