\documentclass[char]{Sel}
\begin{document}
\name{\cSpecter{}}
The "Society of Ethical Liches." What utter poppycock.

You are Specter, a Senior member of the Society of Ethical Liches, but you have no respect for this group's values. You became a lich in the first place by setting fire to a conveniently flammable orphanage. You joined the Society not because you think liches can be "ethical"-- it's a patent oxymoron-- but because you wanted to borrow its respectability when dealing with other magical species. As a Senior member, you have access to many libraries and other resources usually off-limits to your kind, and you cherish that access dearly.

You draw on these resources to pull off exotic magical feats and enhance your power, and now you wish to become Leader of the Society, as the prestige will open even more doors to you. Impressively, you have studied scraps of text across Earth and other worlds to piece together a vampiric spell normally kept secret-- a spell to corrupt a phylactery from afar. The ingredients required are rare and rather temperamental, so you were only able to execute the spell once, a few years back. You targeted Domin, whose power will now be drained at a human's pace, twice as quickly than it should be. You intend to take advantage of the phylactery's weakened state to destroy it, automatically removing Domin from the Society and moving you into the Leader's position. You should either do so secretly, or you should silence Domin forever through straightforward murder, lest you be kicked out from the Society yourself for violating the second rule. Should that plan prove unworkable, you will attempt to become Leader through the official voting procedure-- a difficult task in its own way, but worth the trouble. As Leader, you'll be able to deemphasize Domin's blessed diplomacy, instead throwing the Society's full weight behind your own personal agenda. Never again will the Society sacrifice precious research, as in the Pacific/Atlantic catastrophe. The sheer possibilities dizzy you.

You have already violated the Society's rules in your search for power. In order to run all your different experiments, you have had to expend an extraordinary amount of energy, and so you have used a large variety of magical arts to brutally kill a large variety of humans, whose lifeforces you have subsequently drained. You bring some of the leftover power with you today, in your phylactery, and it's a good thing that the elven lawyers who "monitor" Society members' power levels can be bribed, because your power level has been over 12 for decades. Though you've striven to cover your tracks, rumors swirl, and you'd better avoid drawing suspicion to yourself tonight. Though you try to watch your words, too many of your colleagues are suspicious of you as it is.

You are not the only rulebreaker at this convention, though. According to rumors you've received from elven contacts, one of the members of the Society is not a lich-- you assume they are a fallen lich but did not report the destruction of their phylactery. You intend to discover this imposter out of curiosity. You will then kill this imposter and consume their lifeforce-- undoubtedly a source of great power-- out of your lust for power.

You have one last goal for tonight-- you have long had your eye on Lock and Sollers, both Junior member with a taste for knowledge that rival your own. Sollers will likely capitalize the machine's success and grab a promotion to Senior member, likely putting the resolution in personally, and you went ahead and nominated Lock for a promotion as well. You fully intend to advocate for both their promotions, but you plan to pry some nuggets of knowledge out of them in return. Lock's always had a taste for uncovering practical secrets, while Sollers' interests run more towards theory, like yours. If you can forge an alliance, you might become unstoppable.

\begin{itemz}[Notes]
  \item Your true name is Amorum.
  \item The resolution you submitted immediately pre-game was "Let Lock become Senior member."
      \item Your phylactery currently has 16 units of power. Please fill in the card inside your phylactery's envelope with this information.
   \item While all liches carry booby-trapped magical items with them to deter pickpockets, yours have especially nasty effects. You don't believe they violate the letter of the Society rules, though-- forcing someone to cast a spell has the side effect of draining their power, but surely "draining their power" isn't a direct consequence, is it?
\item You own a booby-trapped Galaxy Note phone, a booby-trapped hundred-dollar bill, a bag of oyster crackers, a Three Musketeers bar, and a phylactery in the form of a paintbrush.
    \end{itemz}
   
    
 \begin{itemz}[Goals]
\item Become Leader
\item Discover the imposter
\item Ally with and promote Lock and Sollers
\item Amass power in every way possible
\end{itemz}


\end{document}
