\documentclass[char]{Sel}
\begin{document}
\name{\cTyran{}}
You have always tried to balance power with justice-- humanity, even. You used your burgeoning sorcerous abilities to work as a vigilante, using magic to track down serial killers and other heinous criminals that the officers of the law, bound by mundane limits, could not find. You murdered them and used those deaths to become a lich.

Even before your transformation, you had heard of Domin’s visionary agenda and aspired to join to the Society of Ethical Liches, so you were thrilled when Domin personally reached out and invited you to become a Junior member. Since then, Domin has become your mentor and a close friend whom you look up to more than ever. You have also grown to like Korv, a powerful if somewhat eccentric Senior member. The third Senior member, Specter, has always made you feel slightly uneasy, though you have never identified why.

You firmly believe in the Society's values, and so you have been glad to welcome newer members into the fold. You have always thought of Sollers as a brilliant inventor, so you're not all that surprised at the announcement of the new charging machine-- you expected nothing less. You liked young Lock as well, when you first met at the last convention. Lock' energy and theatrical flair seemed like a breath of fresh air, a rejuvenating influence that will help keep the Society up-to-date and relevant. You would have never thought Lock capable of grinding another lich into submission.

Yet that is exactly what has happened over the last century. At first sight Korv fell head-over-heels in love with Lock-- you remember the sheer chemistry between them was palpable-- and became Soul Bonded within mere hours. You thought they had found a happy-ever-after at first, but then the rumors started flying throughout the magical community that Lock was treating Korv more like a slave than a lover. Thus a Senior member of the Society was made a laughingstock. It pained you to see such a wise and capable lich brought low, and you swore you would never be so compromised.

Ah, the irony.

You pose as a lawyer nowadays, a devoted public defender, and you were minding your own business and reviewing case files one night when you perceived a sudden burst of raw power-- the sign of a magical mishap. Hoping to provide emergency assistance, you sought out the source and found a toad. 

Clearly, a dark spell had backfired, and you immediately started work on a countercharm. You spoke your incantations and drew on your power and kissed the toad and-- wham!-- suddenly the amphibian was nowhere to see. Instead, a young half-elf-half-human mage stared up you with bewildered eyes. From that first moment you've been half in-love.

You learned that this mage was Carminis, a wayward, rootless orphan, flitting between demiplanes without ever finding anywhere to call home. Yet Carminis is far from a delinquent. In fact, you've never met someone with as much sheer magical potential. Simply being in Carminis' presence is intoxicating.

Carminis has already tapped into that intoxicating potential by accomplishing a feat that even you long considered impossible-- beginning work on a phylactery without shedding a drop of blood. Carminis' intuition claims that it should be possible even to finish the phylactery without murder but that such a process would take many decades, longer than a half-elf-half-human can be expected to naturally live. Yet the two of you both hate the idea of taking lives, and so you became desperate for some alternative.
Carminis stumbled upon a possible solution-- spending time with more liches and observing their spellcasting should provide the necessary insights to speed the phylactery's completion up dramatically. And so you took the risky step of registering Carminis as a member of the Society, in the hopes that the upcoming convention will provide those insights. You will attempt to integrate Carminis well enough into the convention that nobody will wonder about that most basic of Society requirements-- all members must already be liches.

Alas, you wish to protect Carminis from discovery, yet you are growing to fear your attachment to this young sorcerer. What if you end up forming a Soul Bond? No matter how much you’d like to believe that Carminis is currently well-intentioned and will stay that way forever, you have to remember Korv’s plight and grimace-- you didn’t think Lock was so bad either, last convention. You've got to keep Carminis at arm’s length, lest those smiles and that brilliant mind shatter your wavering resolve, and you’ve gone a step further-- you decided you would submit a resolution to focus the next century’s research on breaking Soul Bonds.

Switching your resolution stung a little, because you had hoped to instead nominate yourself for Senior member and throw all your effort into getting that passed. You hope that such a resolution might be proposed anyway, since Domin has been hinting that you're Senior member material for literal ages. Given your commitment to the Society's values and your relative seniority among the Junior members, you both believe you deserve the honor, and you expect Domin would wholeheartedly support your promotion.
Domin has been kind to you from the moment you met, and you return that loyalty, presenting a united front against any threats or usurpers of the Leader’s throne. You don't know quite how to handle the issue of Carminis, though, since all members of the Society ought to be liches and Domin is certainly a stickler for the rules. If Carminis' secret is exposed, you have to hope Domin would set aside the regulations for once and offer protection, since a non-member at this convention is fair game to be killed for power.

So you need to pass your resolution, angle for a promotion if possible, preserve your relationship with Domin and help Carminis without utterly surrendering your heart. You’ve got one last objective tonight-- you want to help Korv in this difficult, and perhaps punish Lock's cruelty.

Damn these Soul Bonds.


\begin{itemz}[Notes]
  \item Your true name is Risus.
  \item The resolution you submitted immediately pre-game was "Let the Society dedicate its research efforts for the next century to dissolving Soul Bonds."
    \end{itemz}
    
 \begin{itemz}[Goals]
\item Help Carminis become a lich
\item Avoid becoming Soul Bonded to Carminis
\item Support Domin and the Society's values
\item Help Korv and punish Lock's cruelty
\end{itemz}


\end{document}
