\documentclass[blue]{Sel}
\begin{document}
\name{\bSociety{}}
\textbf{Society Rules}

Domin, an ancient lich, created the Society of Ethical Liches to provide fellow liches with community and resources and to rehabilitate the species' reputation. Members who wish to join the Society meet with Domin to complete initial admission paperwork, but otherwise members typically do not meet between conventions, except in emergency situations or in cases of ``Soul Bonded''. Society members typically live in the British Isles, as the magical resources afforded by Society membership are clustered there. Such resources include ingredients for complex magic and access to libraries on Earth and in connected demiplanes.

The Society allows any lich to join, provided they agree to follow three core rules:

\begin{enumerate}
\item Members must commit to killing very few humans.
\item Members must treat other members of the Society with respect.
\item Members must attend a Society convention every hundred years and fulfill their voting obligations.
\end{enumerate}

Each of the three rules has been interpreted over time to include more specifics. To comply with Rule 1, liches are expected to kill no more than 4 humans from the start of one convention to the next, except in exceptional self-defense situations which are evaluated on a case-by-case basis. In addition, they are expected to never have power levels above 12. Third-party investigators, usually elven lawyers, check in on the Society's members at random to verify that their power levels are not abnormally high. Every member except the newly-admitted Carminis has been tested at least once over the past century. No member's power level has ever been reported as being above 12.

To comply with Rule 2, members of the Society may not attempt or conspire to steal, corrupt or destroy another member's phylactery. They may not bring items to a convention that are capable of directly reducing another member's power level, affecting their spell-casting abilities, or compromising their phylactery's safety.

To comply with Rule 3, members must arrive promptly at a convention held once every 100 years. In the minutes before a convention begins, every member except the Leader must submit one``resolution'' to be voted on. The Leader must submit {\bf two} resolutions. Resolutions are typically proposals of one of the following kinds:

\begin{enumerate}
\item Proposals that a Junior member be elevated to Senior status. The Junior/Senior/Leader hierarchy is common among magical societies, and Senior members of an upstanding group like the Society are welcomed like honorable dignitaries into assorted libraries, schools and courts that are otherwise off-limits to liches. Senior members cannot be demoted. All new members start off with Junior member status.
\item Proposals for a new research objective. The Society has considerable resources that it devotes to exploring a single research topic every century. The default topic is the process of becoming a lich, as the Society wishes to find a way for humans to become liches without having to commit so many murders in the process. However, studying this topic has never yielded fruit-- some theoreticians speculate it is impossible to reduce the amount of required violence at all-- and members frequently nominate other goals.
\item Proposals for a minor change in how the Society advertises itself to potential recruits. For example, members may stipulate that there will be an extra convention in the coming century, open to potential recruits in order that they might meet members and get a better idea of Society culture. No proposal of this kind has ever passed.
\end{enumerate}

Duplicate proposals will be ignored. Ahead of the convention, members are forbidden from discussing the resolutions they will put forward.

At the start of the convention, resolutions will be anonymously posted in a public location. Liches are expected to spend the convention discussing the resolutions. In the final twenty minutes of a convention, voting occurs.

\textbf{Society History}

Five liches were once members of the Society and are no longer. One withdrew when one of her magical experiments backfired and destroyed her phylactery. One lich asked to be removed from the Society by a convention vote after he decided the anti-violence rules were too restrictive. 

Another lich died after being hunted down and destroyed by a mob of anti-lich human sorcerers in a rare moment when anti-lich stigma turned to open violence. After that, Domin called an impromptu meeting of the Society, and members banded together to track down the culprits, capture them without harming them, and turn them over for discipline to a widely accepted leader among human sorcerers who has a formal alliance with the Society. The Society received praise for its handling of the situation, and anti-lich stigma has been on the decline since then. Still, Society members try to store magical power carefully, so they can be prepared to fight off any such attacks.

The last two liches were entangled in a long-running personal feud, and they were removed from the Society against their will for violating the second rule after trying to openly murder one another during a convention.

When not discussing the resolutions, members amuse themselves by sharing strange stories about the last century they spent pretending to be humans. Debates often arise around the subject of popular culture, as members often disagree strongly over whether the latest music and literary trends are delightful or a sure sign of societal decay. Movies, video games, and the internet may prove excellent conversation starters, since all three have really come into their own since the last convention.

\textbf{Current Society Gossip}

Like any community, the Society has its fair share of rumors and politics. One of the juiciest bits of gossip going around right now concerns a rash of gruesome murders in the British Isles that, according to investigators from other magical species, are the work of a lich. There's no proof a Society lich is personally responsible, but chances are at least one Society member knows something about the crimes, given that all the Society's members are liches currently living in the area.

Another dramatic rumor was confirmed by the invitations to this convention-- last convention, the Society voted to focus a century's worth of research on charging phylacteries without violence, and with the Society's resources, young Sollers has managed such a feat! A talented inventor, Sollers has created a potion-fueled machine that will add energy to liches' phylacteries without requiring any murders, instead drawing on power sources other than lifeforces. The potion inside the machine will brew during most of the convention and is timed to finish up during the last twenty minutes, at which point all phylacteries in Crescent Grove will receive a boost in power. If all goes well, this breakthrough may allow liches to forego violence entirely.

Finally, there was an unusual diplomatic incident recently-- a war broke out among merpeople, and the court of the Pacific Ocean offered the Society of Ethical Liches access to the extraordinary Library of Agartha, buried deep in the core, in exchange for a secret alliance. The Society has historically allied with the court of the Atlantic Ocean, an opponent of the Pacific Court, and so in flagrant violation of diplomatic ethics the Pacific Court asked Domin to use the Society's connections for espionage purposes. Domin immediately refused and exposed the unethical offer to the broader magical community, improving the Society's credibility as a genuinely ethical community but sacrificing a major research opportunity.

The main gossip surrounding the current Society members (listed by length of membership, longest to shortest) is as follows:
\begin{description}
\item [Domin] Founder of the Society and its devoted Leader. Promptly fulfills the Leader's responsibilities, both administrative duties like admitting new members and symbolic duties like reaching out to form bonds with other magical species. Occasionally over-enthusiastic when it comes to enforcing rules and mentoring newer members. Especially fond of Tyran, the most senior Junior member.
\item [Specter] Senior member, known for dabbling in obscure magic. Tends to rub other members the wrong way and end up in arguments.
\item [Korv] Senior member with eccentric tastes. Friends with Tyran, likely because opposites attract. Currently something of a punchline among liches and many others after falling head-over-heels in love with and becoming Soul Bonded to a much younger lich, Lock, at the last Society convention. Rumor has it that Lock has exploited that bond. Has recently been posing as Lock's secretary in the human world.
\item [Tyran] Junior member, known for committing the murders needed to become a lich as a vigilante. Looks up to Domin and considers Korv a good friend. Currently acting as a public defender in human civilization. A confident and eloquent advocate for the Society's values, with a reputation for honesty and personal integrity.
\item [Sollers] Junior member, known for sheer magical brilliance. Will present a machine that can charge phylacteries without violence at this convention.
\item [Lock] Junior member admitted just over a century ago, known primarily as the lich to whom Korv is Soul Bonded. Has used that Soul Bond to personal advantage, rendering Korv a personal servant. Otherwise known for curiosity and a dramatic sense of style. Has been posing as a major CEO.
\item [Carminis] Junior member admitted only a few months ago. Largely unknown even among human sorcerers, despite somehow amassing enough power and kills to become a lich.
\end{description}

\textbf{Crescent Grove}

Previous Society conventions have been held in well-hidden spots on Earth. However, thanks to the organization's growing respectability, Domin was able to negotiate with other magical species to reserve a demiplane named Crescent Grove for this century's meeting. Since liches are rarely welcome on demiplanes, much less one as magically productive as Crescent Grove, the experience will surely be exceptional.

Crescent Grove is populated by pixies, small mischievous creatures that produce pixie dust, a well-known source of magical power. Unfortunately, liches cannot use the energy of pixie dust to power their phylacteries, but they, and all competent sorcerers, can convert concrete deposits of pixie dust into abstract magical knowledge. Using pixie dust thus can provide sorcerers with temporary access to spells they cannot otherwise cast. Such spells are typically silly and harmless, but sometimes they have serious effects, either positive or negative.

Pixies often demand payment in gifts or entertainment in exchange for their dust. They especially like receiving food, money, electronic devices, and items related to the arts.

Electronic devices do not function in Crescent Grove, due to interference from the large concentrations of pixie dust.

Pixies are immune to spells and all other magical effects.


\end{document}
