%%%%%
%%
%% This file sets up the Abil datatype and creates Abil macros.  These
%% are for abilities that characters may have.
%%
%%%%%

\DECLARESUBTYPE{Abil}{Element}
\PRESETS{Abil}{
  \F\MYtext	%% text of ability, read by user
  \F\MYeffect	%% effect text of ability, read by recipient(s)
  }


%%%%%
%% \ability{<name>}{<text>}{<effect>}
%%
%% \ability is a wrapper around \INSTANCE, useful for 1-shot abilities,
%% etc.
\newinstance{Abil}{\ability[3]}{
  \s\MYname{#1}\s\MYtext{#2}\s\MYeffect{#3}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\NEW{Abil}{\aTest}{
%  \s\MYname	{Test Ability}
%  \s\MYtext	{You are a test.}
%  \s\MYeffect	{This is a Test.}
%  }
%
%everyone
\NEW{Abil}{\aLichDetectionSpell}{
  \s\MYname	{Lich Detection Spell (Costs 1 unit of power)}
  \s\MYtext	{Target a creature within 1 ZOC of you. You automatically learn whether the target is a lich or not. Ask a GM for the answer.}
  \s\MYeffect	{You perceive me casting a spell.}
  \suite
  }
  %everyone

  \NEW{Abil}{\aMajorResistanceSpell}{
  \s\MYname	{Major Resistance Spell (Costs 3 units of power)}
  \s\MYtext	{If you cast this within five seconds of being targeted by a Kill Spell or Knock-out Spell, you ignore that spell. If you have been targeted by multiple Kill Spells and/or Knock-out Spells in the last five seconds, this only allows you to ignore one of your choice.}
  \s\MYeffect	{You perceive me casting a spell.}
  \suite
  }
  %everyone

  \NEW{Abil}{\aKillSpell}{
  \s\MYname	{Kill Spell (Costs 5 units of power)}
  \s\MYtext	{Pick a target within 1 ZOC of you and announce out of game that you are targeting them with this spell. It is immediately obvious to all characters who can see or hear you that you are attempting to murder your target. If the target is not a lich, they immediately die.}
  \s\MYeffect	{You perceive me casting a Kill Spell.}
  \suite
  }
  %everyone

  \NEW{Abil}{\aKnockoutSpell}{
  \s\MYname	{Knockout Spell (Costs 2 units of power)}
  \s\MYtext	{Pick a target within 1 ZOC of you and announce out of game that you are targeting them with this spell. It is immediately obvious to all characters who can see or hear you that you are attempting to knock your target unconscious. Your target is knocked out for 5 minutes.}
  \s\MYeffect	{You perceive me casting a Knockout Spell.}
  \suite
  }
  %everyone

  \NEW{Abil}{\aPickpocketSpell}{
  \s\MYname	{Pickpocket Spell (Costs 1 unit of power)}
  \s\MYtext	{Pick a target within a 1 ZOC of you. Tell a GM who your target is. You will receive one item that your target is concealing on their person, chosen at random. If the target is not carrying any items, this spell has no effect. When using this spell, do not announce that you are casting a spell.}
  \s\MYeffect	{You don't see me doing anything.}
  \suite
  }
  %Carminis
  \NEW{Abil}{\aFakeLichAuraSpell}{
  \s\MYname	{Fake Lich Aura Spell (Costs 1 unit of power)}
  \s\MYtext	{For one hour, any Lich Detection Spell targeting you will claim that you are a lich. Tell a GM when you cast this.
  }
  \s\MYeffect	{You perceive me casting a spell.}
  \suite
  }
  %Specter
  \NEW{Abil}{\aDestroyPhylacterySpell}{
  \s\MYname	{Destroy Phylactery Spell (Costs 6 units of power)}
  \s\MYtext	{If you are holding a phylactery, you can target it with this spell. Roll a D20. If your roll is greater than or equal to the amount of power in the phylactery, then you successfully destroy the phylactery. Otherwise, the spell has no effect. If you succeed, take the item card out of the phylactery's envelope and give it to a GM. The item that was previously a phylactery is now a non-magical item.
  }
  \s\MYeffect	{You perceive me casting a spell.}
  \suite
  }
  %Lock
   \NEW{Abil}{\aMinorResistanceSpell}{
  \s\MYname	{Minor Resistance Spell (Costs 1 unit of power)}
  \s\MYtext	{Pick a magical item that is not a phylactery. You can ignore its magical effects for 30 minutes.
  }
  \s\MYeffect	{You perceive me casting a spell.}
  \suite
  }
  
  
  %2 copies, pixie
  \NEW{Abil}{\aPixieDestroyPhylacterySpell}{
  \s\MYname	{Destroy Phylactery Spell (Costs 3 units of power, One-Time Use)}
  \s\MYtext	{If you are holding a phylactery, you can target it with this spell. Roll a D20. If your roll is greater than or equal to the amount of power in the phylactery, then you successfully destroy the phylactery. Otherwise, the spell has no effect. If you succeed, take the item card out of the phylactery's envelope and give it to a GM. The item that was previously a phylactery is now a non-magical item.
  }
  \s\MYeffect	{You perceive me casting a spell.}
  \suite
  }
%1 copy, pixie
    \NEW{Abil}{\aResurrectionSpell}{
  \s\MYname	{Resurrection Spell (Costs 2 units of power, One-time Use)}
  \s\MYtext	{Pick a corpse within 1 ZOC as a target, and they come back to life. This ability can be used once.
  }
  \s\MYeffect	{I cast a powerful spell. The ground rumbles, and you come back to life.}
  \suite
  }
  
 %5 copies with pixies
\NEW{Abil}{\aTruthingSpell}{
  \s\MYname	{Truthing Spell (Costs 1 units of power, One-time Use)}
  \s\MYtext	{For five minutes, you can only say things you believe to be true. Your listeners are sure that you mean what you say during this period.
  }
  \s\MYeffect	{You perceive me casting a spell. For five minutes, you are sure that I believe everything I am saying to be true.}
  \suite
  }
  
   %5 copies with pixies
\NEW{Abil}{\aMusicSpell}{
  \s\MYname	{Music Spell (Costs 1 units of power, One-time Use)}
  \s\MYtext	{For one minute, music of your choice plays. The instrument type is classified as "magic."
  }
  \s\MYeffect	{You perceive me casting a spell. Pretty magical music plays.}
  \suite
  } 
  
     %5 copies with pixies
\NEW{Abil}{\aHaloSpell}{
  \s\MYname	{Halo Spell (Costs 1 units of power, One-time Use)}
  \s\MYtext	{For one minute, an ethereal golden halo hovers over your head.
  }
  \s\MYeffect	{You perceive me casting a spell. An airy golden halo appears above me.}
  \suite
  } 
       %5 copies with pixies
\NEW{Abil}{\aEyeColorSpell}{
  \s\MYname	{Eye Color Spell (Costs 1 units of power, One-time Use)}
  \s\MYtext	{For the rest of the day, your irises change to a color of your choice.
  }
  \s\MYeffect	{You perceive me casting a spell. My eye color changes.}
  \suite
  } 
  
         %2 copies with pixies
\NEW{Abil}{\aEfficiencySpell}{
  \s\MYname	{Efficiency Spell (Costs 2 units of power, One-time Use)}
  \s\MYtext	{For the next fifteen minutes, you can cast spells that require only 1 unit of power without paying the 1-unit cost.
  }
  \s\MYeffect	{You perceive me casting a spell.}
  \suite
  } 
%\NEW{Abil}{\aSpecial}{
%  \s\MYname	{Special Powers}
%  \s\MYtext	{You have special powers, as detailed in your \gTest{}
%		greensheet.}
%  \s\MYeffect	{I have special powers!}
%  \s\MYgreens	{\gTest{}}
%  \suite
%  }
%
%\NEW{Abil}{\aFiremansCarry}{
%  \s\MYname	{Fireman's Carry}
%  \s\MYtext	{You can carry a body as if it were two hands bulky.}
%  \s\MYeffect	{I can carry this body well.}
%  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


  
%% Basic DarkWater-style Martial Attack abilities


%% Everyone alive has these 3
