\documentclass[green]{Sel}
\begin{document}
\name{\gItems{}}
Liches may carry up to five items at a time in their clothing. When an item is in your clothing, you are not touching it, so touch effects are not triggered unless you try to remove it.

If an item is a musical instrument, you can play it. 

Whenever you touch a non-food item you should look inside the corresponding envelope to see if you undergo any magical effects. Non-food items cannot be destroyed unless you know otherwise.

Some magical items have an effect with a specified duration. If you are currently under an item's effect and then you touch the item again, the timer does not restart. For example, imagine that you touch a magical fan that forces you to sing "Happy Birthday" repeatedly for one minute after you touch it. If you touch the fan again thirty seconds later, you still only need to sing "Happy Birthday" for one minute. However, if you touch the fan one more time after one minute has elapsed and the effect has ended, you will need to sing for another full minute.

You may destroy a food item by eating it. If you eat it, destroy the item card. Food items never have magical effects on them.

You cannot tamper with items unless you know otherwise.

You own only the items you are carrying at start of game. Whenever you touch a magical item you own you may choose whether to ignore its magical effect or not.

Besides pixie dust deposits, no two items are identical. This is a kludge.

When a search of a character's clothing occurs, the searcher touches the items with their skin, and the target of the search does not. As a result, if a search reveals magical items, the searcher is affected by the magical items' effects, and the target of the search is not.

\end{document}
